Headgroup structure and cation binding in phosphatidylserine lipid bilayers

### 2019-05-22 Manuscript/manuscriptPS.tex
Small update in the text considering dihedral distrubutions

Interestingly, the three models that best fit the experimental data have a narrower distribution in the C$_\alpha$-C$_\beta$-C$_\gamma$-O$_\gamma$
dihedral angle (single peak around 120$^{\circ}$) in comparison to the other models which yield a distribution between two angles (Fig. \ref{dihedralsHG}).
The restricted motion is also visible in the sampled conformations (Figs.~\ref{HGstructuresPSandPC} (A) and \ref{HGandGLYstructuresPS})
suggesting that the rotation of the carboxyl group is limited in the serine headgroup.
In addition, the N-C$_\beta$-C$_\alpha$-O$_\alpha$ dihedral exhibits a more asymmetric
and narrow angle distribution for PS than for PC headgroup in
CHARMM36 simulations that have the best agreement with experiments
(Figs.~\ref{HGstructuresPSandPC} (B) and \ref{dihedralsHGpc}).
% Also, the sampled conformations of glycerol backbone significantly vary between different simulation models (Figs. \ref{dihedralsGLY}, \ref{HGandGLYstructuresPS}, \ref{dihedralsGLYpc} and \ref{HGandGLYstructuresPSPC}),but further analysis is beyond the scope of this work which focuses on the PS headgroup. There is very little actual information in this statement. The variance was already noted above

>>>>

Interestingly, the three models that best fit the experimental data have a narrower distribution in the C$_\alpha$-C$_\beta$-C$_\gamma$-O$_\gamma$
dihedral angle (single peak around 120$^{\circ}$) in comparison to the other models which yield a distribution between two angles (Fig. \ref{dihedralsHG}).
The restricted motion is also visible in the sampled conformations (Figs.~\ref{HGstructuresPSandPC} (A) and \ref{HGandGLYstructuresPS})
suggesting that the rotation of the carboxyl group is limited in the serine headgroup.
In addition, the N-C$_\beta$-C$_\alpha$-O$_\alpha$ dihedral exhibits a more asymmetric
angle distribution for PS than for PC headgroup in
CHARMM36 and Slipids simulations that have the best agreement with experiments
(Figs.~\ref{HGstructuresPSandPC} (B) and \ref{dihedralsHGpc}).
% Also, the sampled conformations of glycerol backbone significantly vary between different simulation models (Figs. \ref{dihedralsGLY}, \ref{HGandGLYstructuresPS}, \ref{dihedralsGLYpc} and \ref{HGandGLYstructuresPSPC}),but further analysis is beyond the scope of this work which focuses on the PS headgroup. There is very little actual information in this statement. The variance was already noted above
